Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-04 doc/sc2012/code_ex.tex
Reverting changes made earlier for dc state

void distribute_charge(CircuitPiece piece, float dt):
        ROE(piece.rw_pvt), RdA(piece.rn_pvt, piece.rn_shr,piece.rn_ghost) {
  foreach(w : piece.rw_pvt) {
    w#$\rightarrow$#in_node#$\rightarrow$#new_charge += -dt * w#$\rightarrow$#current;
    w#$\rightarrow$#out_node#$\rightarrow$#new_charge +=  dt * w#$\rightarrow$#current;
  }
}

>>>>

void distribute_charge(CircuitPiece piece, float dt):
        ROE(piece.rw_pvt), RdA(piece.rn_pvt,piece.rn_shr,piece.rn_ghost) {
  foreach(w : piece.rw_pvt) {
    w#$\rightarrow$#in_node#$\rightarrow$#new_charge += -dt * w#$\rightarrow$#current;
    w#$\rightarrow$#out_node#$\rightarrow$#new_charge +=  dt * w#$\rightarrow$#current;
  }
}
